---
title: "A Just Vision for Community-Centered Urban Agriculture in Sunset Park"
subtitle: "Brooklyn, NY"
author: 
    - Julianna Mantaay
    - Angelika Wienner
    - Annaliese Tussi
    - Gonzalo Martínez-Herrera

theme: flatly

format: dashboard

---

```{r}
#| label: setup
#| echo: false
#| include: false

library(here)
library(tidyverse)
library(showtext)
library(sf)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE) 

showtext_auto()


# .quarto-dashboard .bslib-value-box .value-box-value {
#     font-size: clamp(.1em, 15cqw, 5em);
# }


```



```{r}
#| label: map-data
#| include: false


# Import Datasets ---------------------------------------------------------

## Shadow data ------------------------------------------------------------

sf_shadow <- st_read(
  dsn = here('1_Data/Spatial/Shadows/sf_shadows_comp.shp')
) |>
  janitor::clean_names() |>
  filter(!st_is_empty(geometry))

## Final backayard subset ------------------------------------------------
sf_final_map <- st_read(
  dsn = here('1_Data/Spatial/Final_Selection/sf_fil_final.shp')
) |>
  janitor::clean_names() |>
  # st_transform(crs = 'EPSG:3857') |>
  filter(!st_is_empty(geometry))


## Flood data


# Flood extreme scenario

sf_taxlot <- st_read(
  dsn = here('1_Data/Spatial/Sunset_Shapefiles/sf_taxlot_bkyn.shp')
) |>
  janitor::clean_names()

sf_flood_ext <- st_read(
  dsn = here("1_Data/Spatial/Flood Risk/GDB/Extreme.gdb/")
) |>
  janitor::clean_names()

sf_flood_ext <- st_crop(x = sf_flood_ext, y = st_bbox(sf_taxlot))

sf_flood_ext$flooding_category <- forcats::as_factor(
  sf_flood_ext$flooding_category
)

sf_flood_ext$flooding_category <- forcats::fct_recode(
  sf_flood_ext$flooding_category,
  "Nuisance flooding (Between 4 in and 1 ft)" = "1",
  "Deep and Contiguous flooding (1 ft or greater)" = "2",
  "Future High Tides (2080)" = "3"
)

# Data Management --------------------------------------------------------

# * Both methods are not keeping the shadow data due to the geometric
# * errors described in the groundthruthing script. I decided to filter
# * the selected backyards from sf_shadow_fil

v_filter_bbl <- sf_final_map$bbl

v_filter_add <- sf_final_map$address

# sf_dash <- filter(sf_shadow,
#   bbl_x %in% v_filter_bbl | address %in% v_filter_add)

sf_dash <- st_join(x = sf_final_map, y = sf_shadow, left = T)

# ! Quita los patios inundables.

v_flood_back <- st_filter(x = sf_final_map, y = sf_flood_ext)

sf_dash <- filter(sf_dash, !objectid %in% v_flood_back$objectid)


# todo resumir datos para cada uno de los patios. Usar summarise y
#  rowwise

sf_shadow_ground <-
  sf_dash |>
  select(objectid, address.x, area, c_ratio, h_shdw_j, h_shdw_s) |>
  # filter(h_shdw_j < 2.5 & h_shdw_s < 1.5) |>
  group_by(objectid, address.x) |>
  summarise(
    Area = round(mean(area), digits = 0),
    'Shade_June (h)' = round(mean(h_shdw_j), digits = 1),
    'Shade_September (h)' = round(mean(h_shdw_s), digits = 1)
  ) |> 
  rename(Address = address.x) |> 
  ungroup()


# ! Elimina algunos de los patios.
sf_shadow_filtered <- sf_dash |>
  select(objectid, address.x, area, c_ratio, h_shdw_j, h_shdw_s) |>
  filter(h_shdw_j < 2.5 & h_shdw_s < 1.5) |>
  group_by(objectid, address.x) |>
  summarise(
    Area = round(mean(area), digits = 0),
    'Shade_June (h)' = round(mean(h_shdw_j), digits = 1),
    'Shade_September (h)' = round(mean(h_shdw_s), digits = 1)
  ) |> 
  rename(Address = address.x) |> 
  ungroup()

# Adds UPROSE point

## Add UPROSE address for reference
v_uprose_point <- st_point(c(983438.9, 177231.3))

sf_uprose_point <- st_sfc(v_uprose_point)

sf_uprose_point <- st_set_crs(sf_uprose_point, value = "EPSG:2263")

sf_uprose <- tibble(id = "UPROSE")

st_geometry(sf_uprose) <- sf_uprose_point

rm(sf_uprose_point, v_uprose_point)


```


# Data Analysis

## Row {height=18%}

### Column 
```{r}
#| content: valuebox
#| title: "Number of backyards"
#| label: num-backyards

list(
  icon = "house-fill",
  color = "primary",
  value = 187
)

```

### Column 

```{r}
#| content: valuebox
#| title: "Average Area"
#| label: avg-area

list(
  icon = "textarea-resize",
  color = "secondary",
  value = "950 ft²" 
)

```

### Column

```{r}
#| content: valuebox
#| title: "Average shade in summer"
#| label: shade-summer

list(
  icon = "brightness-high",
  color = "success",
  value = "3.2 h" 
)

```

### Column

```{r}
#| content: valuebox
#| title: "Average shade in the Fall"
#| label: shade-fall


list(
  icon = "brightness-low",
  color = "warning",
  value = "3.1 h" 
)

```


## Row 

### Column {width=40%}

```{r}
#| label: back-table
#| title: Top 50 Backyards by area and sunlight exposure

sf_top50 <- 
  sf_shadow_ground |>
  arrange(desc(Area), desc('Shade_June (h)'), desc('Shade_September (h)')) |> 
  head(n = 50) |> 
  mutate(Address = str_to_title(Address)) 

sf_top20 <- head(sf_top50, n = 20) 

# Table dataset
sf_top50 |> 
select(-1) |> 
st_drop_geometry() |>
kbl(booktabs = T) |> 
  kable_material() 

```


### Column 

```{r}
#| label: map
#| title: "Sunset Park"

v_pal <- c("deepskyblue", "navy", "gold")

mapview::mapview(sf_flood_ext,
 zcol= "flooding_category",  
 col.regions = v_pal,
 alpha.regions = 0.4,
 layer.name = "Flooding Category", 
 legend = TRUE) +
mapview::mapview(sf_uprose, legend = TRUE) +
mapview::mapview(
  list(sf_shadow_filtered, sf_shadow_ground, sf_top20),
  zcol = list('Shade_June (h)', 'Shade_June (h)', "Shade_June (h)"),
  col.regions = hcl.colors(palette = "Inferno", alpha = 0.8, rev = TRUE, n = 10),
  layer.name = c( "Filtered", "Ground Truth", "Top 20"),
  legend = TRUE,
  map.types = "CartoDB.Positron"
)


```

# About

## Row {.flow}

::: card
::: card-header
About this Project
:::
::: card-body

This dashboard summarizes the spatial analysis main results of the report *A Just Vision for Community-Centered Urban Agriculture in Sunset Park*. The project was developed as a partnership between the [NYC Climate Justice Hub](https://centerforthehumanities.org/project/climate-justice-hub/) and [UPROSE](https://www.uprose.org/).

All data used for the project is public and available at the following sites:

* [NYC Open Data](https://opendata.cityofnewyork.us/)
* [ZoLA](https://zola.planning.nyc.gov/about#9.72/40.7008/-73.733)
* [Department of Environmental Protection](https://www.nyc.gov/site/dep/index.page)
* [Federal Emergency Management Agency (FEMA)](https://www.fema.gov/)
* [MapPLUTO](https://www.nyc.gov/content/planning/pages/resources/datasets/mappluto-pluto-change)
* Shadow data available at: [https://osf.io](https://osf.io/4tqp9/files/osfstorage)

:::
:::

::: card
::: card-header
About the Research Team
:::
::: card-body

**Project Team 2025-2026**

* Juliana Maantay -Project Lead
* Angelika Winner – Project Co-Lead
* Annaliese Tucci – Research Assistant
* Gonzalo Martínez – Research Assistant
* Matilda Curley - Research Intern
* Nebraska Hernández – UPROSE Hub Advocate


**Project Team 2023-2024**

* Juliana Maantay – Project Lead
* Daniel Shtob - Support Lead
* Angelika Winner – Research Assistant
* Enrique Valencia - Research Assistant
* Jada Macharie – Research Assistant
* Nebraska Hernández – UPROSE Hub Advocate

:::
:::